\qhead{1. Your company. Describe your company, the main products sold, the type of clients (B2B, B2C, local, worldwide, etc.) and the main competitors. Indicate the product(s) the answers focus on.}

BYD started out as a battery manufacturer in 1995, and today it is the largest maker of new-energy vehicles in the world. In 2025 it passed Tesla in battery-electric volume, selling roughly 2.25 million of them on revenue close to RMB~804 billion \parencite{byd2025}. What really sets the company apart is how much of each car it builds itself. Somewhere between 70 and 80 percent of the components, the batteries, motors, power chips and platforms, are made in-house, and that gives BYD a cost advantage over Tesla that analysts put at around 15 percent \parencite{motleyfool2025}. With something like 110{,}000 engineers behind it, this cost base is the thing that makes every pricing choice in the rest of this paper possible.

The customers are almost entirely private consumers, and the company sells worldwide rather than only at home. China is still the core market, but Europe and several emerging markets matter more each year, and alongside the retail buyers there is a steady flow of fleet and taxi sales. In China the cars go through franchised dealers, while in Europe BYD increasingly runs its own showrooms.

The range climbs a long way. It begins with the Seagull at under RMB~60{,}000, runs up through the mass-market Dynasty and Ocean cars, and finishes with the premium Denza and Fang Cheng Bao brands and the Yangwang badge at the very top, where the U9 reaches about three million dollars \parencite{electrekU9}. That is close to a 370-fold spread of prices under one roof.

For the answers that follow I concentrate on the BYD Qin Plus DM-i, the mass-market plug-in hybrid the company sells under the line ``electricity cheaper than oil'' \parencite{carscoopsQin}, and I bring in the wider range only where a question needs it. Its rivals fall into three groups: Tesla as the direct global competitor, the petrol carmakers such as Toyota and Volkswagen that BYD is trying to convert, and the hundred or more domestic Chinese brands it is fighting in a long price war.
