\qhead{3. Price Structure and Market Segmentation. How does your company segment markets? Explain the rationale and the resulting prices.}

BYD splits its buyers by how much they are willing to pay, and it does so using all three of the levers the course sets out \cite{nagle2018}.

The most visible lever is the shape of the offer itself. The brand ladder is about as clear a good, better, best structure as you will find anywhere. It starts with the Seagull from about \euro7{,}300, moves up through the Dynasty and Ocean cars below \euro38{,}000, then the Denza between \euro38{,}000 and \euro64{,}000, the Fang Cheng Bao above that, and finally Yangwang above \euro100{,}000 and reaching close to \euro2.7 million. Someone shopping for a Yangwang will never look at a Seagull, so the top of the ladder lets BYD collect the surplus of wealthy buyers while the bottom still serves the price-sensitive ones.

The second lever is the way the product is measured and charged for. By telling the Qin story in terms of running cost rather than sticker price, ``electricity cheaper than oil'', BYD quietly shifts the comparison onto total cost of ownership, and that lifts what people will pay.

The third lever is the set of fences that keep the segments apart, and BYD uses several of the standard types. A stripped trim with no smart driving is a product-design fence that nudges keener buyers upward. The free ``God's Eye'' system, sold in three grades tied to the brand level, is a versioning or product-line fence, since the computing power and sensor count justify the gap between tiers \cite{insidechinaADAS}. China versus Europe is a location fence that holds European prices far above Chinese ones, the subject of question twelve. And the separate Yangwang badge is a buyer-identification fence that sorts the status buyers on its own.

The reasoning behind all of this is simple enough. A fence only works if it stops the high-paying customer from slipping down to the low price without making anyone feel cheated, and BYD manages that because every rung really is a different car rather than the same car behind an artificial barrier. The result is that the company captures value right across the demand curve instead of settling on one middle price, which would give too much away at the top and shut people out at the bottom. Bundling reinforces the versioning fence here, because building the driver-assistance system into the car rather than selling it on its own means a buyer cannot strip it out to reach a lower price.
