\qhead{5. Choosing Prices Levels. Which price levels does your company apply? What are the main considerations in that decision?}

The interesting thing about BYD is that it does not settle on a single price level. It runs several at once, each suited to a different part of the range \parencite{nagle2018}.

At the bottom, with cars like the Seagull and the Dynasty, the strategy is penetration. The conditions the course lists are all present. Demand is very sensitive to price, the scale and the learning that come with vertical integration keep pushing unit costs down, and the company is chasing market share, dealer coverage and the network effects of being everywhere. The reason penetration works here rather than simply losing money is that BYD's cost really is lower than its rivals', so a price near cost for BYD is still above cost even when it sits below what others can manage.

At the top the logic flips to skimming. The Yangwang U9 sells for something like three million dollars \parencite{electrekU9}. Almost nobody buys one and demand barely moves with price, which is the point, because the car exists to show off the technology and to recover research spending. Europe sits in between, priced just under Tesla and Volkswagen rather than at rock bottom, which lets BYD keep a margin the tariff protects.

Underneath all three sits the same window. The lowest sensible price is the extra cost of building the car, held down by the Blade Battery, and the highest is the exchange value against the local rival. Because BYD's cost edge stretches that window wider than anyone else's, it has room to choose penetration without ever dropping below cost, and that is a freedom its higher-cost competitors do not share.

None of this is without risk. Penetration teaches buyers to expect cheap cars and is hard to reverse, and the 19 percent fall in net profit during 2025, even as volumes hit records, shows the strain, with regulators stepping in on top \parencite{byd2025}. The sensible long-term move, which is already starting to show, is to walk customers up the ladder toward the dearer, more differentiated cars before the price war and the authorities force the change.
