\qhead{7. Costs and Their Relation with Pricing; Financial Implications of Price Changes. What changes in costs have greater implications in terms of price changes for your company? Explain why.}

For a pricing decision only the incremental costs count, the ones that change when another car is built, while sunk research and shared overhead do not \parencite{nagle2018}. On that basis the cost that matters most to BYD is the battery cell, because the battery is the single biggest variable item in an electric car. The Blade Battery saves roughly ten euros per kilowatt-hour against the older cells \parencite{motleyfool2025}, and that saving drops straight into the contribution margin, the price minus the variable cost, which in turn lowers how far the price can fall.

Why this dominates becomes clear from the break-even sales change, which asks how much extra volume a price cut needs just to stand still on profit. Take a car at RMB~100{,}000 with a variable cost of 80{,}000, so the margin is 20{,}000, or 20 percent. Cut the price by 10 percent and the formula gives a break-even of plus 100 percent: BYD would have to double its sales merely to hold profit steady. Now suppose a cheaper battery lifts the margin to 30{,}000. The same cut now needs only 50 percent more volume. The lesson is that a lower variable cost shrinks the volume a cut requires, so the identical price cut that would be suicidal for a higher-cost rival, whose thinner margin demands an even larger and unreachable jump in sales, is merely painful for BYD. That is the mechanism by which the cost edge turns into a weapon.

Price is also the strongest lever on profit, since a one percent change in price tends to move operating profit by something like 8 to 11 percent, far more than a one percent change in volume. BYD felt this in reverse in 2025, when net profit fell 19 percent on record revenue \parencite{byd2025} as small concessions across millions of cars added up. The blow was softened because the fatter overseas margins help carry the fight at home, but the episode shows that it is movements in the relevant incremental cost, not headline volume, that really set how far BYD can cut.
