\qhead{9. The Impact of Competition Upon Prices — What structural conditions most affect your pricing? How?}

The Chinese EV market is a \textbf{repeated prisoner's dilemma}: each firm gains share by cutting price (defect), but if all cut, every firm lands in the mutual-loss cell of falling industry profit \parencite{nagle2018}. BYD's 19\% profit fall is that cell \parencite{byd2025}. In a repeated game cooperation can be sustained through tacit collusion — but only when the market's structural conditions support it, and here they mostly do not.

The conditions that most affect BYD's pricing are precisely those that \textbf{block} tacit collusion:

\begin{itemize}[nosep,leftmargin=1.3em]
  \item \textbf{Many competitors} (100+ NEV brands): coordination is hard and defection hard to monitor.
  \item \textbf{Asymmetric costs}: BYD's cost edge means it does \emph{not} share rivals' interest in high prices — it profits from a low-price equilibrium that bankrupts them, breaking the ``commonality of interests'' collusion requires.
  \item \textbf{Overcapacity and slowing growth}: pressure to cut prices to fill plants.
  \item \textbf{Transparent prices}: cuts are detected instantly, triggering rapid retaliation and escalation.
\end{itemize}

\textbf{How this shapes BYD — the asymmetric-cost twist.} Tacit collusion needs \emph{similar} firms with a common break-even point. Because BYD is the low-cost outlier, the defection--retaliation logic inverts: it can sustain a low-price equilibrium that punishes rivals more than itself, so \textbf{defection is its dominant long-run strategy} and any cut it makes is credibly permanent. No stable cartel-like equilibrium can form, the price war persists, and — tellingly — it is the \emph{government}, through anti-``involution'' pressure and Pricing-Law reform, that has had to do the disciplining the rivals cannot. The structural takeaway: competition shapes BYD's pricing less through what rivals charge and more through the fact that BYD's cost asymmetry makes the cooperative outcome unreachable.
