\qhead{10. Price Leadership and Price Wars. Is there a price leader in your industry? How does it perform its role? Are the others followers or challengers? Do you see potential for a price war?}

BYD is a price leader, but only of a peculiar sort. Good leadership in the course's sense needs three things, visibility, a common motivation with the rest of the industry, and the resolve to follow through \cite{nagle2018}. BYD has the visibility, since it is the biggest and most closely watched player, and it certainly has the resolve, because when it cuts it sustains the cut. What it lacks is the common motivation. Its cost advantage means it actually wants lower prices than its rivals do, so instead of leading the industry upward, the stabilising job a leader is supposed to do, it leads it downward, setting off fresh rounds of cuts of more than 30 percent on some models in May 2025 \cite{restofworldWar}. The others are reluctant followers rather than challengers, because matching BYD eats into their thinner margins faster than it eats into BYD's.

A wider war is already here, and the warning signs are nearly all flashing: growth has stalled, there is too much capacity, manufacturing carries heavy fixed costs, the mass-market cars are hard to tell apart, buyers chase price, and everyone can see everyone else's prices.

So should a higher-cost legacy carmaker fight back on price? Working through the usual questions, the cut is real and broad, a lot of volume is exposed, and BYD clearly wants both share and the exit of weaker rivals, but the legacy firm cannot sustain the war because its break-even, as question seven showed, is far worse. The honest answer is not to match on price at all, and instead to lean on the things price cannot touch, stronger differentiation, a retreat to a defensible premium corner, or simply leaving the cheap end of the market, since against a lower-cost attacker the higher-cost firm is the one that breaks first.

Was BYD right to start it? The conditions that justify starting a war mostly fit, a real cost advantage, a price-driven market, and the stamina to outlast others. Yet there are still no real winners. BYD's own profit fell 19 percent and the regulators moved in \cite{byd2025}, which is precisely why its smartest way out is to drift back toward value-based, differentiated pricing. If it did want to calm the market, the course points less to force than to signalling, announcing openly that it sees no gain in further cuts and letting rivals lift prices first to test whether a truce will hold.
