\qhead{11. Legal and Ethical Issues on Pricing. What are your company's main ethical challenges concerning pricing? How do they affect pricing practices? Does your company face legal cases, and do you see potential for such challenges?}

There are really three different accusations to weigh, and the course's taxonomy of objectionable pricing helps keep them apart \cite{nagle2018}.

The first is predatory pricing, the charge that the prices are too low. The economic test asks whether price sits below average variable cost and whether the firm intends to recoup once rivals are gone. BYD's prices are low, but it still earns a positive gross margin of roughly 17 to 20 percent, so below-cost is hard to show, and recoupment is unproven. Its cost edge means a low price is not the same thing as a price below cost, so for BYD specifically the behaviour is aggressive rather than illegal.

The second accusation is dumping or unfair subsidy, and this one has actually bitten. The European Union's anti-subsidy investigation led to countervailing duties of 17 percent on BYD, the lowest of the firms it sampled and well below the 35.3 percent placed on SAIC, running for five years from October 2024 \cite{ec2024}. The objection there is to the subsidised cost base rather than to BYD's own conduct, and it feeds straight back into practice by pushing the company to build cars inside Europe.

The third is the ethical question, and here the picture is genuinely mixed. On a utilitarian reading, cheap electric cars raise welfare and cut emissions. On a fairness reading, European producers see subsidised pricing as unfair and Chinese rivals see the cuts as destructive, which is why Beijing has publicly attacked the ``involution'' of below-cost selling and moved to reform its Pricing Law \cite{cnbcInvolution}. And on a self-interest reading, the 19 percent fall in profit suggests even BYD's own long-run health is at stake \cite{byd2025}. This is the old argument between maximising shareholder value within the law and weighing the wider stakeholders, with the state taking the stakeholder side. Looking ahead, the real exposure is in Europe: if BYD ever became dominant, crossing the rough 40 percent mark, then Article 102 on abuse of a dominant position, which covers both predatory pricing and price discrimination, would apply, a sharper rule than anything in US law.
