\qhead{12. Open Question. The most important pricing topic for your company not covered above: geographic price discrimination (China versus Europe).}

The pricing topic that matters most to BYD and that the other answers only touch on is geographic price discrimination, selling much the same car at very different prices in different markets and using location itself as the fence \cite{nagle2018}.

The numbers make the point. A Seagull goes for about \euro7{,}200 in China \cite{electrekSeagull}, while in Europe the cheapest BYD, the Dolphin Surf, starts near \euro19{,}990. The effect shows up in the margins, an overseas gross margin of 28.1 percent against 17.2 percent at home in 2025 \cite{byd2025}. Europe is where the money is made, and China is where the share is fought over.

The reason the gap holds is that geography, the different technical approvals each market demands, and the EU tariff together make arbitrage impractical, since a buyer cannot simply ship a Chinese Seagull to Germany. Within each market the prices still fall inside a sensible band that tariffs, freight, the local cost of selling and the nearest rival's price can all explain, which is ordinary behaviour rather than anything that needs correcting.

The tariff is part of the story too. The 17 percent duty raises what it costs BYD to land a car in Europe, but because Europeans will pay so much more, measured against Tesla and Volkswagen, the margin survives anyway. The answer is the new Hungarian plant, which builds the cars inside the bloc, sidesteps the tariff, shortens the supply line and protects that European price band \cite{fortuneHungary}, and selling more through its own showrooms lets BYD hold a firm price rather than discount the margin away.

The reason I single this out is that geographic discrimination is generally lawful and often improves welfare by serving more buyers, limited only by Article 102 if BYD were to become dominant, and more practically because this margin gap is the engine that pays for the price war back home. Without that cross-subsidy from Europe, the penetration pricing the earlier answers described would not hold together.